Practical Security Log Book

### 2016-02-20 logbook.tex
Tidied up log book

\begin{lstlisting}[language=bash]
$ sudo apt-get install gnupg
[...]
$
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ gpg --list-keys
gpg: directory `/home/ross/.gnupg' created
gpg: new configuration file `/home/ross/.gnupg/gpg.conf' created
gpg: WARNING: options in `/home/ross/.gnupg/gpg.conf' are not yet active during this run
gpg: keyring `/home/ross/.gnupg/pubring.gpg' created
gpg: /home/ross/.gnupg/trustdb.gpg: trustdb created
$
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ gpg --gen-key
gpg (GnuPG) 1.4.12; Copyright (C) 2012 Free Software Foundation, Inc.
This is free software: you are free to change and redistribute it.
There is NO WARRANTY, to the extent permitted by law.

@@

After answering all the questions and providing a passphrase,
you may be asked to generate some entropy.
Machines have a hard time using a good source of randomness to make sure
the key is not predictable and guessable, so you may be required to do
some work via keystrokes, mouse movements or run some processes that
do disk activity. Once this is complete, you will have your public and
private key pair.

@@

\begin{lstlisting}[language=bash]
$ gpg --list-keys
/home/ross/.gnupg/pubring.gpg
-----------------------------
pub   4096R/B8D85C76 2014-12-14
uid                  Ross Fenning <gpg@rossfenning.co.uk>
sub   4096R/CEEFF134 2014-12-14
$
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ gpg --list-secret-keys
/home/ross/.gnupg/secring.gpg
-----------------------------
sec   4096R/B8D85C76 2014-12-14
uid                  Ross Fenning <gpg@rossfenning.co.uk>
ssb   4096R/CEEFF134 2014-12-14
$
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ gpg --output mypublickey.gpg --export B8D85C76
$
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ gpg --armor --export B8D85C76
-----BEGIN PGP PUBLIC KEY BLOCK-----
Version: GnuPG v1.4.12 (GNU/Linux)

@@

\begin{lstlisting}[language=bash]
$ gpg --import mypublickey.pgp
gpg: key B8D85C76: public key "Ross Fenning <gpg@rossfenning.co.uk>" imported
gpg: Total number processed: 1
gpg:               imported: 1  (RSA: 1)
$
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ gpg --fingerprint B8D85C76
pub   4096R/B8D85C76 2014-12-14
      Key fingerprint = BDFD 1EF9 9052 4326 BA89  3897 30BC 9067 B8D8 5C76
uid                  Ross Fenning <gpg@rossfenning.co.uk>
sub   4096R/CEEFF134 2014-12-14

@@

\begin{lstlisting}[language=bash]
$ gpg --sign-key B8D85C76

@@

\begin{lstlisting}[language=bash]
$ gpg --output B8D85C76-signedby-12345678.gpg  --export B8D85C76
$
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ gpg --import B8D85C76-signedby-12345678.gpg
gpg: key B8D85C76: "Ross Fenning <gpg@rossfenning.co.uk>" 1 new signature
gpg: Total number processed: 1
gpg:         new signatures: 1
gpg: 3 marginal(s) needed, 1 complete(s) needed, PGP trust model
gpg: depth: 0  valid:   1  signed:   0  trust: 0-, 0q, 0n, 0m, 0f, 1u
$
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ echo "Hello" >secret.txt
$ cat secret.txt 
Hello
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ echo "Hello" >secret.txt
$ cat secret.txt 
Hello
\end{lstlisting}

\begin{lstlisting}[language=bash]
$ gpg --recipient B8D85C76 --encrypt secret.txt
gpg: checking the trustdb
gpg: 3 marginal(s) needed, 1 complete(s) needed, PGP trust model
gpg: depth: 0  valid:   2  signed:   1  trust: 0-, 0q, 0n, 0m, 0f, 2u
gpg: depth: 1  valid:   1  signed:   0  trust: 1-, 0q, 0n, 0m, 0f, 0u
gpg: next trustdb check due at 2015-04-20
$ ls secret.txt*
secret.txt  secret.txt.gpg
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$ gpg --decrypt secret.txt.gpg

@@

The setup here is a network of virtual machines running under Virtualbox
running on a host computer that can be isolated if necessary. Once the
setup has been designed, we will look at using Vagrant to make a repeatable
way of bootstrapping the lab on demand. This will help if we ever feel the
need to tear down the entire setup and start afresh or to share the
configuration with other researchers.

@@

Kali is a GNU/Linux distribution based on Debian that comes with hundreds
of tools preinstalled that can be used in cracking and penetration testing. It
is available to download as an ISO CD image file which can easily be used
to install in a virtual machine using Virtualbox.

@@

Metasploitable is a pre-built virtual machine from Rapid 7 to aid with learning
its penetration testing tool, Metasploit. We can equally make use of this
for learning Kali. As with Kali, we can add a configuration to our Vagrantfile
(appendix~\ref{appendix:vagrant}) for a pre-built box for convenience. Other
Packer-based builds are available on Github\footnote{https://github.com/waratek/vagrant-boxes}
if it is again preferred to have more control over the build.

@@

\begin{lstlisting}[language=bash]
vagrant@metasploitable:~$ route
Kernel IP routing table
Destination     Gateway         Genmask         Flags Metric Ref    Use Iface
192.168.51.0    *               255.255.255.0   U     0      0        0 eth0
vagrant@metasploitable:~$
\end{lstlisting}

@@

>>>>

\begin{lstlisting}
$ sudo apt-get install gnupg
[...]
$
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --list-keys
gpg: directory `/home/ross/.gnupg' created
gpg: new configuration file `/home/ross/.gnupg/gpg.conf' created
gpg: WARNING: options in `/home/ross/.gnupg/gpg.conf' are not yet active during this run
gpg: keyring `/home/ross/.gnupg/pubring.gpg' created
gpg: /home/ross/.gnupg/trustdb.gpg: trustdb created
$
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --gen-key
gpg (GnuPG) 1.4.12; Copyright (C) 2012 Free Software Foundation, Inc.
This is free software: you are free to change and redistribute it.
There is NO WARRANTY, to the extent permitted by law.

@@

After answering all the questions and providing a passphrase,
you may be asked to generate some entropy.
Machines have a hard time using a good source of randomness to make sure
the key is not predictable and guessable, so you may be required to do
some work via keystrokes, mouse movements or run some processes that
do disk activity to generate some random events from which entropy
can be derived. Once this is complete, you will have your public and
private key pair.

@@

\begin{lstlisting}
$ gpg --list-keys
/home/ross/.gnupg/pubring.gpg
-----------------------------
pub   4096R/B8D85C76 2014-12-14
uid                  Ross Fenning <gpg@rossfenning.co.uk>
sub   4096R/CEEFF134 2014-12-14
$
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --list-secret-keys
/home/ross/.gnupg/secring.gpg
-----------------------------
sec   4096R/B8D85C76 2014-12-14
uid                  Ross Fenning <gpg@rossfenning.co.uk>
ssb   4096R/CEEFF134 2014-12-14
$
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --output mypublickey.gpg --export B8D85C76
$
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --armor --export B8D85C76
-----BEGIN PGP PUBLIC KEY BLOCK-----
Version: GnuPG v1.4.12 (GNU/Linux)

@@

\begin{lstlisting}
$ gpg --import mypublickey.pgp
gpg: key B8D85C76: public key "Ross Fenning <gpg@rossfenning.co.uk>" imported
gpg: Total number processed: 1
gpg:               imported: 1  (RSA: 1)
$
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --fingerprint B8D85C76
pub   4096R/B8D85C76 2014-12-14
      Key fingerprint = BDFD 1EF9 9052 4326 BA89  3897 30BC 9067 B8D8 5C76
uid                  Ross Fenning <gpg@rossfenning.co.uk>
sub   4096R/CEEFF134 2014-12-14

@@

\begin{lstlisting}
$ gpg --sign-key B8D85C76

@@

\begin{lstlisting}
$ gpg --output B8D85C76-signedby-12345678.gpg  --export B8D85C76
$
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --import B8D85C76-signedby-12345678.gpg
gpg: key B8D85C76: "Ross Fenning <gpg@rossfenning.co.uk>" 1 new signature
gpg: Total number processed: 1
gpg:         new signatures: 1
gpg: 3 marginal(s) needed, 1 complete(s) needed, PGP trust model
gpg: depth: 0  valid: 1  signed: 0  trust: 0-, 0q, 0n, 0m, 0f, 1u
$
\end{lstlisting}

@@

\begin{lstlisting}
$ echo "Hello" >secret.txt
$ cat secret.txt 
Hello
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --recipient B8D85C76 --encrypt secret.txt
gpg: checking the trustdb
gpg: 3 marginal(s) needed, 1 complete(s) needed, PGP trust model
gpg: depth: 0  valid: 2  signed: 1  trust: 0-, 0q, 0n, 0m, 0f, 2u
gpg: depth: 1  valid: 1  signed: 0  trust: 1-, 0q, 0n, 0m, 0f, 0u
gpg: next trustdb check due at 2015-04-20
$ ls secret.txt*
secret.txt  secret.txt.gpg
\end{lstlisting}

@@

\begin{lstlisting}
$ gpg --decrypt secret.txt.gpg

@@

The setup here is a network of virtual machines running under Virtualbox\footnote{https://www.virtualbox.org/}
running on a host computer that can be isolated if necessary. Once the
setup has been designed, we will look at using Vagrant\footnote{https://www.vagrantup.com/}
to make a repeatable
way of bootstrapping the lab on demand. This will help if we ever feel the
need to tear down the entire setup and start afresh or to share the
configuration with other researchers.

@@

Kali\footnote{https://www.kali.org/}
is a GNU/Linux distribution based on Debian that comes with hundreds
of tools preinstalled that can be used in cracking and penetration testing. It
is available to download as an ISO CD image file which can easily be used
to install in a virtual machine using Virtualbox.

@@

Metasploitable\footnote{http://sourceforge.net/projects/metasploitable/}
is a pre-built virtual machine from Rapid 7 to aid with learning
its penetration testing tool, Metasploit. We can equally make use of this
for learning Kali. As with Kali, we can add a configuration to our Vagrantfile
(appendix~\ref{appendix:vagrant}) for a pre-built box for convenience. Other
Packer-based builds are available on Github\footnote{https://github.com/waratek/vagrant-boxes}
if it is again preferred to have more control over the build.

@@

\begin{lstlisting}
vagrant@metasploitable:~$ route
Kernel IP routing table
Destination   Gateway  Genmask        Flags Metric Ref  Use  Iface
192.168.51.0  *        255.255.255.0  U     0      0      0  eth0
vagrant@metasploitable:~$
\end{lstlisting}

@@

\printbibliography
